Appendix

### 2025-10-21 manuscript_rmarkdown/manuscript.Rmd
Rework of empirical central normality test to include outlier rate, and kappa.

central_normality_lookup_table <- .get_test_statistic_lookup_table(
  manuscript_dir = manuscript_dir,
  k = 0.80,
  outlier_rate = 0.00,
  for_manuscript = FALSE
)

empirical_central_normality_lookup_table <- .get_test_statistic_lookup_table(
  manuscript_dir = manuscript_dir,
  k = 0.80,
  for_manuscript = FALSE
)

>>>>

ecn_lookup_table <- .get_test_statistic_lookup_table(
  manuscript_dir = manuscript_dir
)

usethis::use_data(
  ecn_lookup_table,
  two_sided_function_parameters, 
  internal = TRUE, 
  overwrite = TRUE
)
```

### 2025-10-21 manuscript_rmarkdown/manuscript_appendix.Rmd
Rework of empirical central normality test to include outlier rate, and kappa.

Critical values for the central normality test and its empirical variant are
found in Table \ref{tab:central-normality-critical-statistic} and Table 
\ref{tab:empirical-central-normality-critical-statistic}, respectively.

@@

```{r empirical-central-normality-critical-statistics, warning=FALSE, message=FALSE, fig.cap=cap, fig.height=2.5}
cap <- paste0(
  "Critical test statistic $\\tau_{\\alpha, n, \\kappa = 0.80}$ of the (empirical) ",
  "central normality test as function of $n$ for several values of significance level $\\alpha$. ",
  "The critical test statistics for central normality test are determined using fully normal data, ",
  "whereas the statistics for the empirical variant are determined using centrally normal data, ",
  "i.e. with fully normal data where 10% of elements are replaced by outliers. ",
  "emp: empirical"
)

>>>>

Critical values for the empirical central normality test are
found in Table \ref{tab:central-normality-critical-statistic} and Table 
\ref{tab:empirical-central-normality-critical-statistic}, respectively.

@@

```{r empirical-central-normality-critical-statistics, warning=FALSE, message=FALSE, fig.cap=cap, fig.height=2.5}
cap <- paste0(
  "Critical test statistic $\\tau_{\\alpha, n, \\kappa = 0.80, \\zeta}$ of the empirical ",
  "central normality test as function of $n$ for several values of significance level $\\alpha$. ",
  "emp: empirical"
)
